Predict Models

### 2024-01-03 scripts/generate_RF_models_copy.Rmd
predict too slow, need to reduce feature using caret::rfe

cores <- parallel::detectCores()
lapply(splicies[3:335], modeller)

>>>>

cores <- parallel::detectCores()
lapply(splicies[1], modeller)

```{r}
x <- filter(train_dat, taxon==  'Asclepias cryptoceras' )

  species <- sf::st_drop_geometry(x) %>% 
    dplyr::pull(taxon)
  species <- species[1]
  x1 <- terra::extract(layers, x)

  x_dat <- cbind(x$Occurrence, x1) %>% 
    dplyr::mutate(Occurrence = as.factor(`x$Occurrence`)) %>% 
    dplyr::select(-ID, -`x$Occurrence`) %>% 
    dplyr::relocate(Occurrence, .before = 1) %>% 
    dplyr::filter(if_all(2:ncol(.), ~ !is.na(.)))

  trainIndex <- caret::createDataPartition(x_dat$Occurrence, p = .8, 
                                           list = FALSE, times = 1)
  TRAIN <- x_dat[ trainIndex,]
  TEST  <- x_dat[-trainIndex,]

  library(caret)

TRAIN <- Boruta_var_selector(TRAIN)

ctrl <- rfeControl(functions = rfFuncs,
                   method = "repeatedcv", repeats = 5)

floor((ncol(TRAIN)-1)*0.1)*10 # upper subset
subsets = c(30, 25, 20, 15, 10)

rfProfile <- rfe(TRAIN[,2:ncol(TRAIN)], TRAIN$Occurrence,
                 sizes = subsets,
                 rfeControl = ctrl)

# accept a percent change with less than -1.5% 
results <- rfProfile[['results']] %>% 
    mutate(pct_change = (Accuracy/lead(Accuracy) - 1) * 100)

predictors(rfProfile)
plot(rfProfile)

v_no <- filter(results, pct_change > -1.5) %>% 
  # identify all selections which performed well relative to maximal model 
  slice_min(Variables, n = 1) %>%  # now identify the one with the fewest variables
  pull(Variables)

rfProfile[["variables"]] %>% 
  filter(Variables == v_no) %>% 
  group_by(var) %>% 
  summarise(imp = mean(Overall)) %>% 
  arrange(-imp) # tri, slope, cfvo_30_60, phh2o_0_5, ngd10

### 2024-01-03 scripts/predict_models.Rmd
predict too slow, need to reduce feature using caret::rfe

  pout <- '../results/suitability_maps'
  layers <- terra::subset(layers, term_grab(sdm))
  layer_subset <- terra::crop(rast(layers, bound)
  terra::predict(
    type = 'prob', cores = 16,
    layer_subset, sdm, cpkgs="randomForest",
    filename = file.path(pout, paste0(x$species, '.tif')),
    wopt = c(names = 'predicted_suitability'))

@@

setGDALconfig(c("GDAL_MAX_DATASET_POOL_SIZE"),  c(""))

lapply(models_occ[c(5)], predict_wrapper)
```

>>>>

  pout <- '../results/suitability_maps'
  layer_subset <- terra::subset(layers, term_grab(sdm))
  layer_subset <- terra::crop(layer_subset, bound)

  return(layer_subset)
  #terra::predict(
  #  type = 'prob', cores = 16,
  #  layer_subset, sdm, cpkgs="randomForest",
  #  filename = file.path(pout, paste0(x$species, '.tif')),
  #  wopt = c(names = 'predicted_suitability'))

@@

ob <- lapply(models_occ[c(5)], predict_wrapper)
ob1 <- ob[[1]]
ob1

predict_wrapper(models_occ[[5]])
```
